---
title: "Experiment Report"
author: "Kadir Korkmaz"
date: "December 4, 2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
  fig_width: 6 
  fig_height: 2 
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)


dataFolderName <- "2020-12-08_13:08:40"

# Folder which contains *.stat files
dataFolderPath <- paste( "/home/kadir/Git/experiment-automation/output/stats/", dataFolderName, sep="")

# Lists all stat files
list_of_files <- list.files(path = dataFolderPath, recursive = TRUE, pattern = "\\.stat$",  full.names = TRUE)

# Read all data from stat files, and adds a column as FileName
experiment_df <- list_of_files %>%
  set_names(.) %>%
  map_df(read_table2,  .id  = "FileName")

experiment_df$FileName <- basename(experiment_df$FileName)


colnames(experiment_df)[2] = "Date"
colnames(experiment_df)[3] = "Time"
colnames(experiment_df)[4] = "Type"
colnames(experiment_df)[5] = "Round"
colnames(experiment_df)[6] = "BlockPropagation"
colnames(experiment_df)[7] = "BAWithOutFinalStep"
colnames(experiment_df)[8] = "BAWithFinalStep"
colnames(experiment_df)[9] = "ConsensusType"
colnames(experiment_df)[10] = "BlockType"
colnames(experiment_df)[11] = "BlockHash"


```



#Experiment Setup and Configuration

Two nucs are connected over LAN. 50 Algorand process is deployed per nuc. Each process is using Trickle to cap the upload and download bandwidth 20Mbs each.
TC rules are not used to add delay! Block and Vote validation disabled. Block size is 1MB.

Dataset name is **`r dataFolderName`**

The number of rows is **`r nrow(experiment_df)`**

Maximum round number is **`r max(experiment_df$Round)`**


```{r, echo=FALSE}

experiment_df %>% 
  group_by(FileName) %>%
  summarise(
    #count = n(), 
    mean_bp = mean(BlockPropagation, na.rm=TRUE)
  )


summary( experiment_df$BlockPropagation )




```


\newpage
# Overal Results

```{r, echo=FALSE}

boxplot(experiment_df[6:8],
  main = "",
  xlab = "Step",
  ylab = "Seconds",
  col = "orange",
  border = "brown",
  horizontal = FALSE,
  notch = FALSE
)

```




\newpage
# Block Propagation Statistics

```{r, echo=FALSE}

hist(experiment_df$BlockPropagation, main="", xlab = "")

```

```{r, echo=FALSE}

boxplot(experiment_df$BlockPropagation,
  main = "",
  xlab = "Seconds",
  ylab = "Block Propagation",
  col = "orange",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

```

\newpage
# BA Elapsed Time Without Final Step Statistics


```{r, echo=FALSE}

hist(experiment_df$BAWithOutFinalStep, main="", xlab = "")

```

```{r, echo=FALSE}

boxplot(experiment_df$BAWithOutFinalStep,
  main = "",
  xlab = "Seconds",
  ylab = "BA Without Final Step",
  col = "orange",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

```



\newpage
# BA Elapsed Time With Final Step Statistics

```{r, echo=FALSE}

hist(experiment_df$BAWithFinalStep, main="", xlab = "")

```

```{r, echo=FALSE}

boxplot(experiment_df$BAWithFinalStep,
  main = "",
  xlab = "Seconds",
  ylab = "BA With Final Step",
  col = "orange",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

```




